We are not the 99 percent: quantifying asphericity in the distribution of Local Group satellites

### 2018-02-07 paper/paper.tex
new plots physical characteristics
edit

Among the three simulations, the results infered from ELVIS data show
the lowest fraction of M31 and MW systems; for Illustris1-Dark we have
the highest fraction of M31/MW systems. The results from Illustris1
are in between these two, actually closer to ELVIS.

@@

%MW mass
%https://arxiv.org/abs/1407.1078
\newpage

@@

\begin{figure*}
\centering
\includegraphics[width=0.30\textwidth]{scatter_random_ranked_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_ranked_illudm_width.pdf}
\includegraphics[width=0.30\textwidth]{scatter_norm_ranked_illudm_width.pdf}
\caption{
\label{fig:physical}}
\end{figure*}

>>>>

Among the three simulations, the results infered from ELVIS data show
the lowest fraction of M31 and MW systems; for Illustris1-Dark we have
the highest fraction of M31/MW systems. The results from Illustris1
are in between these two, but closer to ELVIS.

The most probable reason for these trends is the different median mass
for the MW/M31 halos in the pairs from these simulations. 
For instance for the MW halo the median maximum circular velocity is
$\sim 160$ \kms, $\sim 150$ \kms and $\sim 120$ \kms in the ELVIS,
Illustris1 and Illustris1-Dark simulations, respectively.
For the M31 halo this median velocity is $\sim 200$\kms both for the
ELVIS and Illustris1 simulations, while for the Illustris1-Dark it is
$\sim 160$ \kms.

@@

%MW mass
%https://arxiv.org/abs/1407.1078

@@

\begin{figure}
\centering
\includegraphics[width=0.34\textwidth]{int_distro_LG_v_rad.pdf}
\includegraphics[width=0.34\textwidth]{int_distro_LG_d.pdf}
\includegraphics[width=0.34\textwidth]{int_distro_M31_vmax.pdf}
\includegraphics[width=0.34\textwidth]{int_distro_MW_vmax.pdf}
\caption{Physical characteristics of the LG pairs selected in the
  simulations. All lots show the integrated distributions. The
  physical properties are the radial comoving velocity between the MW
  and M31, the radial separation between the MW and M31 and the
  maximum circular velocity for the M31 and MW dark matter halo.
\label{fig:physical}}
\end{figure}
